\thetitle

### 2013-09-29 tfpie/tfpie.tex
Blah about types.

\begin{enumerate}
\item Explicit representation of unions and interfaces in the
  language.  Previously, interfaces were simply described in stylized
  comments, following the \htdp approach.
\item Types are now specified as part of the program and are (statically)
  enforced.
\item Java syntax is substantially different and more verbose. For
  example, constructors must be defined explicitly.
\item The testing environment is somewhat different, and requires
  additional boilerplate, although we are
  able to use the JavaLib framework~\cite{local:java-world} to support testing with
  structural equality.
\end{enumerate}

>>>>

\begin{enumerate}
\item Explicit representation of unions and interfaces in the
  language.  Previously, interfaces were simply described in stylized
  comments, following the \htdp approach.
\item Types are now specified as part of the program and are
  (statically) enforced.  Data definitions and interfaces can be
  transformed from the stylized comments into {\tt interface}
  definitions and method signatures annotated with types.  Students
  are taught the benefits of type systems, which impose syntactic
  restrictions sufficient to prove objects meet (the structural
  aspects of) their interface definitions.  Students also encounter
  the downside of types when they discover the type system cannot
  always follow valid reasoning about program invariants and may reject
  perfectly good programs.
\item Java syntax is substantially different and more verbose. For
  example, constructors must be defined explicitly.
\item The testing environment is somewhat different, and requires
  additional boilerplate, although we are
  able to use the JavaLib framework~\cite{local:java-world} to support testing with
  structural equality.
\end{enumerate}
